Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-25 writing/DraftExposurePaper/DraftExposurePaper.Rmd
add ike data

>>>>

```{r}
#library(data.table)
#ike_gauge <- read.csv("/Users/joshuaferreri/Documents/ike_rain.csv", header = TRUE)
#save(ike_gauge, file = "writing/DraftExposurePaper/ike_gauge.RData")
load("ike_gauge.Rdata")
ike_nldas <- county_rain(counties = unique(ike_gauge$fips),
                             start_year = 2008, end_year = 2008,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
ike_nldas <- ike_nldas %>%
        filter(storm_id == "Ike-2008")
ike_gauge$fips <- as.character(ike_gauge$fips)
compare_rain <- right_join(ike_nldas, ike_gauge, by = "fips")
#alex_nldas <- as.data.table(alex_nldas)
#alex_gauge <- as.data.table(alex_gauge)
#compare_rain <- left_join(alex_nldas, alex_gauge, by = "fips")
b <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw()
b
```
